% !TEX program = xelatex
\documentclass[11pt, a4paper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}

% Identifying information
\newcommand{\FirstName}{Zachary}
\newcommand{\LastName}{Batist}
\newcommand{\Initials}{Z}
\newcommand{\MyName}{\FirstName\ \LastName}

\newcommand{\Email}{zacharybatist@gmail.com}
\newcommand{\PersonalWebsite}{zackbatist.info}
\newcommand{\MyGitHub}{zackbatist}
\newcommand{\Twitter}{@mtl\_zack}
\newcommand{\Mastodon}{archaeo.social/@zackbatist}
\newcommand{\ORCID}{0000-0003-0435-508X}
%\newcommand{\Address}{4653 Rue Clark \\ Montreal, Quebec, Canada \\ H2T 2T3}
\newcommand{\Address}{\phantom{text} \\ \phantom{text} \\ \phantom{text}}
\newcommand{\UTorontoAddress}{Bissell Building, 140 St. George Street \\ M5S 3G6, Toronto, Ontario, Canada}
\newcommand{\Affiliation}{\TORINF \\ \TOR}
\newcommand{\TORINF}{Faculty of Information}
\newcommand{\Title}{Curriculum Vit\ae}
%\newcommand{\LabWebsite}{compgeolab.org}

% Names for citing coauthors
\newcommand{\Me}{\LastName, \Initials}
\newcommand{\CostisDallas}{Dallas, C}
\newcommand{\ValMasters}{Masters, V}
\newcommand{\TiffanyTorma}{Torma, TC}
\newcommand{\NielFerris}{Ferris, N}
\newcommand{\IstoHuvila}{Huvila, I}
\newcommand{\SeamusRoss}{Ross, S}
\newcommand{\MichaelCarter}{Carter, WM}
\newcommand{\TristanCarter}{Carter, T}
\newcommand{\DanContreras}{Contreras, D}
\newcommand{\CiaraZogheib}{Zogheib, C}
\newcommand{\KatieCampeau}{Campeau, K}
\newcommand{\YosefGarfinkel}{Garfinkel, Y}
\newcommand{\KatharinaStreit}{Streit, K}
\newcommand{\KyleFreund}{Freund, KP}
\newcommand{\ShawnGraham}{Graham, S}
\newcommand{\NehaGupta}{Gupta, N}
\newcommand{\JoleneSmith}{Smith, J}
\newcommand{\AndreasAngourakis}{Angourakis, A}
\newcommand{\AndrewReinhard}{Reinhard, A}
\newcommand{\KateEllenberger}{Ellenberger, K}
\newcommand{\JoelRivard}{Rivard, J}
\newcommand{\BenMarwick}{Marwick, B}
\newcommand{\BethCompton}{Compton, B}
\newcommand{\RobBlades}{Blades, R}
\newcommand{\CristinaWood}{Wood, C}
\newcommand{\GaryNobles}{Nobles, G}
\newcommand{\JoeRoe}{Roe, J}
\newcommand{\DRosenberg}{Rosenberg, D}
\newcommand{\YorkRowan}{Rowan, Y}
\newcommand{\MartinLoignon}{Loignon, M}
\newcommand{\WeiminMiao}{Miao, W}
\newcommand{\LianggaoHu}{Hu, L}
\newcommand{\AndrewBier}{Bier, A}
\newcommand{\TarekBismar}{Bismar, TA}
\newcommand{\JamesScrivens}{Scrivens, PJ}
\newcommand{\KorenMann}{Mann, K}
\newcommand{\MarkBasik}{Basik, M}
\newcommand{\AmelieBouchard}{Bouchard, A}
\newcommand{\PierreFiset}{Fiset, PO}
\newcommand{\GeraldBatist}{Batist, G}

% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.11\textwidth}@{\hspace{0.02\textwidth}}p{0.88\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{\newline \aiDoi\ \href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{\newline \faGithub\ \href{https://github.com/#1}{\detokenize{#1}}}
\newcommand{\Gist}[1]{\newline \faGithub\ \href{https://gist.github.com/#1}{#1}}
\newcommand{\Website}[1]{\newline \faGlobe\ \href{https://#1}{#1}}
\newcommand{\ZenodoDOI}[1]{\newline \aiZenodo\ \href{https://doi.org/#1}{#1}}
% \newcommand{\Slides}[1]{\newline \faStickyNote\ \href{https://#1}{#1}}
\newcommand{\OA}{\aiOpenAccess\enspace}
\newcommand{\Invited}{\newline • \textbf{Invited talk}}
\newcommand{\Role}[1]{\newline • Role: #1}
\newcommand{\Preprint}[1]{\newline \faParagraph\ \href{https://doi.org/#1}{#1}}
\newcommand{\Note}[1]{\newline \faExclamationCircle\ {#1}}
\newcommand{\Youtube}[1]{\newline • Recording: \faYoutube\ \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}


% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{9pt}{0}\selectfont #1 -- #2}
\newcommand{\Year}[1]{\fontsize{9pt}{0}\selectfont #1}
% \newcommand{\DurationOngoing}[2]{\fontsize{10pt}{0}\selectfont #1 -- \newline \fontsize{8pt}{0}\selectfont Present}
% \newcommand{\DurationAbandoned}[2]{\fontsize{10pt}{0}\selectfont #1 -- \newline \fontsize{8pt}{0}\selectfont Abandoned}
\newcommand{\Ongoing}{\fontsize{8pt}{0}\selectfont present}
\newcommand{\Abandoned}{\fontsize{8pt}{0}\selectfont abandoned}
%\newcommand{\Ongoing}{$\ast$}
\newcommand{\Future}{future}
\newcommand{\Review}{In review}
\newcommand{\Press}{In press}
\newcommand{\Progress}{In progress}
\newcommand{\Accepted}{accepted}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3 \newline #4}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[a4paper,margin=1.5cm,includehead,headsep=2mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
\usepackage{fontspec}  % required to make older xelatex compile with UTF8

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.5cm}\bfseries\fontsize{12pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.2cm}\mdseries\fontsize{12pt}{0}\selectfont\uppercase}

% Set the spacing for sections
%\usepackage{titlesec}
%\titlespacing{\section}{0pt}{0cm}{0.3cm}
%\titlespacing{\subsection}{0pt}{0.3cm}{0.3cm}

% Disable number of sections. Use this instead of "section*" so that the sections still appear as PDF bookmarks. Otherwise, would have to add the table of contents entries manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
  \fontsize{10pt}{12pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
  \hspace{0.2cm} -- \hspace{0.2cm}
  \monthyear\today
}
\rhead{\fontsize{10pt}{0}\selectfont \thepage/\pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{multicol}

\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
{\fontsize{22pt}{0}\selectfont\MyName}\\[-1.5cm]
\begin{minipage}[t]{1\textwidth}
  \begin{flushright}
    % Last updated: \monthyear\today\\
    Website: \href{https://\PersonalWebsite}{\PersonalWebsite}\\
    ORCID: \href{https://orcid.org/\ORCID}{\ORCID}\\
    Email: \href{mailto:\Email}{\Email}
    %GitHub: \href{https://github.com/\MyGitHub}{\MyGitHub}\\
    % Mastodon: \href{https://\Mastodon}{\Mastodon}\\
    % Twitter: \href{https://\Twitter}{\Twitter}
  \end{flushright}
\end{minipage}\\[0.1cm]
\rule{\textwidth}{0.2pt}\\[-1cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Professional Appointments}

% \begin{EntriesTable}
%   \Duration{2018}{\Ongoing}  &
%   \Appointment{Affiliate Researcher}{\UHEARTH}{\SOEST}{\UHM, USA}
%   \\
%   \Duration{2017}{2018}  &
%   \Appointment{Visiting Research Scholar}{\UHEARTH}{\SOEST}{\UHM, USA}
%   \\
%   \Duration{2014}{2018}  &
%   \Appointment{Assistant Professor}{Departamento de Geologia Aplicada}{Faculdade de Geologia}{\UERJ, Brazil}
% \end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Areas of Expertise}
\vspace{-2em}
\begin{multicols}{2}
  \begin{itemize}
      \item Digital archaeology methods
      \item Scholar of scientific practice
      \item Research data management
      \item Open archaeology infrastructure
      \item Scientific software development
      \item Qualitative data analysis
      \item Meta-research
      \item Network analysis
      
  \end{itemize}
\end{multicols}

\vspace{-2em}
\section{Current Position}
\vspace{-1em}
\begin{EntriesTable}
  \Duration{2025}{} &
  \textbf{Postdoctoral Researcher}
  \newline
  Covid-19 Immunity Task Force Databank
  \newline
  Department of Epidemiology, Biostatistics and Occupational Health
  \newline
  School of Public and Global Health, McGill University
  \Website{zackbatist.info/CITF-Postdoc}
  \GitHub{zackbatist/CITF-Postdoc}\\[-0.5cm]
\end{EntriesTable}

\vspace{-1em}
\section{Education}
\vspace{-1em}
\begin{EntriesTable}
\Year{2023}  &
  \textbf{PhD}, Faculty of Information, University of Toronto
  \newline
  \href{https://tspace.library.utoronto.ca/handle/1807/130306}{Archaeological data work as continuous and collaborative practice}
  \\
\Year{2014}  &
  \textbf{MA}, Department of Anthropology, McMaster University
  \newline
  \href{https://macsphere.mcmaster.ca/handle/11375/16528}{Obsidian Circulation Networks in Southwest Asia and Anatolia: A Comparative Approach}
  \\
\Year{2012}  &
  \textbf{BA}, Directed Interdisciplinary Studies, Carleton University
  %\newline
  %Feasting In Bronze Age Greece: A Network Analysis Approach
  \\
\Year{2009}  &
  \textbf{DEC}, Social Sciences, Dawson College\\[-0.5cm]
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1em}
\section{Past positions}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2018}{2023}  &
  \textbf{Research Assistant}
  \newline
  E{\textendash}CURATORS: Pervasive Digital Curation Activities, Objects and Infrastructures in Archaeological Research and Communication
  \newline
  Faculty of Information, University of Toronto
  \\
\Duration{2016}{2021}  &
  \textbf{Database Manager}
  \newline
  Stelida Naxos Archaeology Project
  \\
% \Year{2009}  &
%   \textbf{Research Assistant}
%   \newline
%   Redpath Museum, McGill University
%   \\
\Duration{2007}{2009}  &
  \textbf{Research Assistant}
  \newline
  Molecular Pharmacology Laboratory
  \newline
  Lady Davis Institute for Medical Research\\[-0.5cm]
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Outcomes}
\vspace{-1em}
\subsection{Journal articles}
\vspace{-1em}
\begin{EntriesTable}
  \Year{2025}  &
  \Me.
  \textbf{Balancing situated and objective representations in archaeological fieldwork.}
  Advances in Archaeological Practice.
  13(4):514-527.
  \DOI{10.1017/aap.2025.10101}
  \GitHub{zackbatist/fuzzy-concrete}
  \Website{zackbatist.info/fuzzy-concrete} (postprint)
\\
\Year{2025}  &
  \Me.
  \textbf{Locating creative agency in archaeological data work.}
  \newline
  Peer Community in Archaeology.
  \DOI{10.17613/8eqy4-n1m82}
  \GitHub{zackbatist/locating-creative-agency}
  \Website{zackbatist.info/locating-creative-agency} (postprint)
\\
\Year{2024}  &
  \Me.
  \textbf{Does not compute! Accounting for social and situated experiences while integrating and analyzing obsidian sourcing data.}
  Archeologia e Calcolatori. (special issue comprising papers presented at ArcheoFOSS XVII).
  35(2):47-54.
  \DOI{10.19282/ac.35.2.2024.06}
\\
\Year{2024}  &
  \Me.
  \textbf{On the Value of Informal Communication in Archaeological Data Work.}
  Open Archaeology.
  10(1):20240014.
  \DOI{10.1515/opar-2024-0014}
\\
\Year{2024}  &
  \Me { \&} \JoeRoe.
  \textbf{Open archaeology, open source? Collaborative practices in an emerging community of archaeological software engineers.}
  Internet Archaeology
  67.
  \DOI{10.11141/ia.67.13}
  \GitHub{zackbatist/openarchaeo-collaboration}
  % \Website{zackbatist.info/openarchaeo-collaboration} (postprint)
  % \ZenodoDOI{10.5281/zenodo.12752060}
\\
\Year{2023}  &
  \Me { \&} \JoeRoe.
  \textbf{Open-archaeo: a resource for documenting archaeological software development practices.}
  Journal of Open Archaeology Data.
  11(9):1-7.
  \DOI{10.5334/joad.111}
  \\
\Year{2021}  &
  \Me, \ValMasters, \TiffanyTorma, \NielFerris, \IstoHuvila, \SeamusRoss, \MichaelCarter { \&} \CostisDallas.
  \textbf{Figurations of Digital Archaeological Practice in Two Mediterranean Fieldwork Projects.}
  Open Archaeology (Special Issue on Archaeological Practice on Shifting Grounds)
  7(1):1731-1755.
  \DOI{10.1515/opar-2020-0217}
  %\ZenodoDOI{10.5281/zenodo.5831760}
  \\
\Year{2021}  &
  \DanContreras, \Me, \CiaraZogheib { \&} \TristanCarter.
  \textbf{Matching Pragmatic Lithic Analysis and Proper Data Architecture: The QuARI R Shiny Database Interface.}
  Advances in Archaeological Practice
  9(4):299-311.
  \DOI{10.1017/aap.2021.11}
  \GitHub{zackbatist/QuARI}
  \\
\Year{2017}  &
  \TristanCarter, \Me, \KatieCampeau, \YosefGarfinkel { \&} \KatharinaStreit.
  \textbf{Investigating Pottery Neolithic Socio-Economic “Regression” in the Southern Levant: Characterising Obsidian Consumption at Sha’ar Hagolan (N. Israel).}
  Journal of Archaeological Science: Reports
  15:305-317.
  \DOI{10.1016/j.jasrep.2017.08.016}
  \\
\Year{2014}  &
  \KyleFreund { \&} \Me.
  \textbf{Sardinian Obsidian Circulation and Early Maritime Navigation in the Neolithic as Shown through Social Network Analysis.}
  Journal of Island and Coastal Archaeology
  9(3):364-380.
  \DOI{10.1080/15564894.2014.881937}
  \\
\Year{2009}  &
  \MartinLoignon, \WeiminMiao, \LianggaoHu, \AmelieBouchard, \TarekBismar, \JamesScrivens, \KorenMann, \MarkBasik, \PierreFiset, \Me { \&} \GeraldBatist.
  \textbf{Frequent Nrf2 depletion due to Cul3 overexpression in breast cancer is associated with sensitivity to carcinogens, oxidative stress and chemotherapy.}
  Molecular Cancer Therapeutics
  8(8):2432-2440.
  \DOI{10.1158/1535-7163.MCT-08-1186}
\end{EntriesTable}

\newpage
\subsubsection{Articles in Progress}
\vspace{-1em}
\begin{EntriesTable}
\Year{\Progress}  &
  \Me, Julie Lund { \&} Isak Roalkvam
  \textbf{Bibliometric analysis of Viking Age Research.}
  \newline
  \emph{A project whose goal is to identify trends in the published archaeological literature corresponding with shifting attitudes concerning the origins of the Viking Age.}
  % \GitHub{zackbatist/BibVik}
  % \Website{https://zackbatist.info/BibVik/manuscript}
\\
\Year{\Progress}  &
Bernier, A., Baltzan, I., Wey, T., \Me. { \&} Fortier, I.
  \textbf{Data Governance in Longitudinal Mother-Child Cohorts: An Empirical Assessment of the Canadian ReACH Studies.}
  \newline
  \emph{Compares data use conditions that distinct research teams assign to their datasets.}
\\
\Year{\Progress}  &
  \Me, Ouellet, M., Murphy, T. { \&} Buckeridge, D.
  \textbf{CITF Databank Emails Analysis.
  }
  \newline
  \emph{Investigates the invisible labour of research data sharing through analysis of operational email correspondence.}
% \\
% \Year{\Review}  &
%   \textbf{Worldwide Innovative Network (WIN) Consortium: Building a Common Global Cancer Database}
%   Nature Reviews in Clinical Oncology.
%   \newline
%   \emph{Investigates the invisible labour of research data sharing through analysis of operational email correspondence.}
  % \\
% \Year{\Progress}  &
%   \Me.
%   \textbf{The situation of data papers in archaeological knowledge production.}\newline
%   \emph{Traces how published archaeological datasets are situated within broader citation networks, through empirical analysis of open bibliometric metadata.}
% \\
% \Year{\Progress}  &
%   \JoeRoe { \&} \Me.
%   \textbf{Archaeology in the fediverse: reclaiming ownership of scholarly social media.}\newline
%   \emph{Position paper articulating the discussion held during our panel at ArcheoFOSS XVII.}
% \\
% \Year{\Progress}  &
%   \CITF Team { \&} \Me.
%   \textbf{CITF Databank marker paper}\newline
%   \emph{Marker paper outlining the CITF Databank.}
\\
\Year{\Progress}  &
  \Me { \&} Shirin Abbasinejad Enger.
  \textbf{Positive mentorship in the history of radiology.
  % (Title TBD)
  }\newline
  \emph{Concerned with positive leadership in academic research environments, through the historical example of Stefan Meyer, Professor and Director of the Radium Institute in Vienna, who mentored several prominent women scientists during the interwar period.}
\end{EntriesTable}

\vspace{-2em}
\subsection{Book contributions}
\vspace{-1em}
\begin{EntriesTable}
\Year{2018}  &
  \ShawnGraham, \NehaGupta, \JoleneSmith, \AndreasAngourakis, \AndrewReinhard, \KateEllenberger, \Me, \JoelRivard, \BenMarwick, \MichaelCarter, \BethCompton, \RobBlades, \CristinaWood { \&} \GaryNobles.
  \textbf{The Open Digital Archaeology Textbook.}
  eCampus Ontario.
  \Website{o-date.github.io}\newline
  \faIcon{award}\ Award for Outstanding Work in Digital Archaeology, Archaeological Institute of America
\end{EntriesTable}

\subsection{Conference proceedings}
\begin{EntriesTable}
\Year{\Review}  &
  \Me.
  \textbf{Data Management is People Management: On Abstraction of Data and Labor in Archaeological Projects.}
  Data and Technology Politics in Archaeology Workshop.
  % \newline
  % \emph{Critically evaluates the mediating devices that occur throughout the continuum of archaeological practice, and characterizes them as points of convergence where collaborative commitments are reified and reproduced.}
  \GitHub{zackbatist/data-tech-poli-arch}
  \Website{zackbatist.info/data-tech-poli-arch}
\\
\Year{2022}  &
  \Me.
  \textbf{Documenting archaeological knowledge construction as information practices.}
  Human History and Digital Future. Proceedings of the 46th Conference on Computer Applications and Quantitative Methods in Archaeology.
  Tübingen University Press.
  \DOI{10.15496/publikation-94869}
  \\
\end{EntriesTable}

\vspace{-2em}
\subsection{Open-source Software}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2020}{2021} &
  \textbf{Queryable Artefact Record Interface (QuARI)}
  \newline
  A database interface designed to facilitate the irregular, iterative, and non-linear workflows that are commonly employed in lithic analysis.
  \GitHub{zackbatist/QuARI}
\end{EntriesTable}

\vspace{-2em}
\newpage
\subsection{Open Datasets}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2018}{\Ongoing}  &
  \textbf{open-archaeo}
  A comprehensive list of open source archaeological software and resources.
  \DOI{10.5281/zenodo.8299651}
  \GitHub{zackbatist/open-archaeo}
  \Website{open-archaeo.info}
  \\
\Duration{2014}{2017}  &
  \textbf{The Database of Obsidian Sourcing Studies (DObsiSS)}
  A listing of chemically characterized archaeological obsidian, compiled from published journal articles, excavation reports, conference papers and other scholarly records.
  \DOI{10.5281/zenodo.55848}
  \GitHub{zackbatist/DObsiSS}
  \Website{zackbatist.info/DObsiSS}
\end{EntriesTable}

\subsection{Other Open Initiatives}
\vspace{-1em}
\begin{EntriesTable}
  \Duration{2025}{\Ongoing}  &
    \textbf{Digital Archaeology Maintainathon}
    A week-long drive to encourage maintenance of code and data, and to help instill good para-coding practices among archaeological researchers.
    \GitHub{sslarch/maintainathon}
    \Website{https://sslarch.github.io/maintainathon/}
\\
  \Duration{2024}{\Ongoing}  &
    \textbf{Diamond Open Archaeology}
    A listing of diamond open access archaeology journals.
    \DOI{10.5281/zenodo.15026607}
    \GitHub{open-archaeo/diamond}
    \Website{diamond.open-archaeo.info}
% \\
%   \Duration{2025}{\Abandoned}  &
%   \textbf{open-archaeo/ai}
%   A community-led and collaboratively built survey of AI applications in archaeology, which emphasizes how AI methods relate to other and existing archaeological practices, including research ethics and open science.
%   Currently abandoned / in stasis.
%   \GitHub{open-archaeo/ai}
%   \Website{ai.open-archaeo.info}
\end{EntriesTable}

\vspace{-3em}
\section{Awards \& Honors}
\vspace{-1em}
\begin{EntriesTable}
\Year{2014}  &
  \textbf{Robert P. Wolff Thesis Prize}
  \newline
  Society for Philosophy \& Culture, McMaster University
  \\
\Year{2012}  &
  \textbf{Dean's Honour List}
  \newline
  Carleton University
  \\
\Year{2012}  &
  \textbf{Michael Kelway Oliver Scholarship}
  % (\$2000)
  \newline
  Carleton University
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3em}
\section{Grants \& Fellowships}
\vspace{-1em}
\subsection{Major Grants}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2019}{2021}  &
  \textbf{SSHRC Doctoral Fellowship}. Archaeological data curation as continuous and collaborative practice. Award ID: {752-2019-2233}. (\$20,000)\\[-0.5cm]
\end{EntriesTable}
\subsection{Minor Grants}
\vspace{-1em}
\begin{EntriesTable}
\Year{2019}  &
  \textbf{Research Travel Grant} (\$500)
  \newline
  Faculty of Arts and Science, University of Toronto
  \\
\Year{2017}  &
  \textbf{Joseph and Maria Shaw Graduate Student Travel Award} (\$500)
  \newline
  The Archaeology Centre, University of Toronto
  \\
\Year{2015}  &
  \textbf{McMaster University Travel Scholarship for OpenCon 2015} (\$2500)
  \newline
  McMaster University Library, McMaster University
  \\
\Year{2015}  &
  \textbf{Edith M. Wightman Travel Scholarship} (\$1000)
  \newline
  School of Graduate Studies, McMaster University
  \\
\Year{2015}  &
  \textbf{Travel Assistance Grant} (\$500)
  \newline
  School of Graduate Studies, McMaster University
  \\
\Year{2015}  &
  \textbf{Graduate Student Travel Award} (\$120)
  \newline
  Archaeological Institute of America
  \\
\Year{2014}  &
  \textbf{McMaster University Travel Scholarship for OpenCon 2014} (\$2500, declined)
  \newline
  McMaster University Library, McMaster University
  \\
\Year{2011}  &
  \textbf{Full Tuition Scholarship} (declined)
  \newline
  Digital Humanities Summer Institute, University of Victoria
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newpage
\section{Teaching}
\vspace{-1em}
\subsection{Teaching Assistant}
\vspace{-1em}
\begin{EntriesTable}
\Year{2020}  &
  \textbf{Curatorial Practice}
  (MSL 2000)
  \newline
  Faculty of Information, University of Toronto
  \\
\Duration{2017}{2020}  &
  \textbf{Representing, Documenting, and Accessing the Cultural Record}
  (INF 1321)
  \newline
  Faculty of Information, University of Toronto
  \\
\Year{2017}  &
  \textbf{Information Policy, Regulation and Law}
  (INF 2181)
  \newline
  Faculty of Information, University of Toronto
  \\
\Year{2016}  &
  \textbf{Archaeology and Popular Culture}
  (ANTH 2PC3)
  \newline
  Department of Anthropology, McMaster University
  \\
\Duration{2014}{2015}  &
  \textbf{World Archaeology}
  (ANTH 2WA3E)
  \newline
  Department of Anthropology, McMaster University
  \\
\Year{2012, 2015}  &
  \textbf{Introduction to Anthropology: Identity, Race and Power}
  (ANTH 1AB3E)
  \newline
  Department of Anthropology, McMaster University
  \\
\Year{2013}  &
  \textbf{Introduction to Anthropology: Sex, Food and Death}
  (ANTH 1AA3)
  \newline
  Department of Anthropology, McMaster University
\end{EntriesTable}

\vspace{-2em}
\subsection{Workshops \& Short Courses}
\vspace{-1em}
\begin{EntriesTable}
\Year{2022 \newline\footnotesize{March}}  &
  \textbf{Using Qualitative Data Analysis Software}
  \newline
  The Ethnography Lab Methods Café: Software in Ethnographic Research Methods
  \newline
  Department of Anthropology, University of Toronto
  \\
\Year{2018 \newline\footnotesize{January}}  &
  \textbf{Designing and Implementing Relational Databases}
  \newline
  Archaeological Information Interest Group
  \newline
  The Archaeology Centre, University of Toronto
  \GitHub{zackbatist/archaeo-db-workshop}
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Student supervision}
% \subsection{P\lowercase{h}D \lowercase{(main advisor)}}
% \begin{EntriesTable}
% \Duration{2021}{\Ongoing}  &
%   India Uppal
%   \newline
%   \LIV, UK.
%   \newline
%   Co-advisors: Vanderlei C. Oliveira Jr., Richard Holme
% \end{EntriesTable}

% \subsection{P\lowercase{h}D \lowercase{(co-advisor)}}
% \begin{EntriesTable}
% \Duration{2021}{\Ongoing}  &
%   Gelson Ferreira de Souza Junior
%   \newline
%   Universidade de São Paulo, Brazil.
%   \newline
%   Advisor: Ricardo I.F. Trindade
%   \\
% \Duration{2017}{2022}  &
%   Santiago R. Soler
%   \newline
%   Universidad Nacional de San Juan, Argentina.
%   \newline
%   Advisor: Mario E. Gimenez
% \end{EntriesTable}

% \subsection{Master's}
% \begin{EntriesTable}
% \Duration{2020}{2021}  &
%   Aidan Hernaman
%   \newline
%   \LIV, UK.
% \end{EntriesTable}

% \subsection{Undergraduate}
% \begin{EntriesTable}
% \Duration{2021}{2022}  &
%   Sarah Askevold, Laura Nicholls, and Hamed R.H. Al-Salehi
%   \newline
%   \LIV, UK.
%   \\
% \Duration{2020}{2021}  &
%   Majed M.A. Abura, Ali A.A. Alhazmi, Daniel P. Gilbert, and Mustafa M.M.
%   Alordowny
%   \newline
%   \LIV, UK.
%   \\
% \Duration{2019}{2020}  &
%   Lottie Cooper, Steven Heer, Charles Thomson, and Alexander Borges
%   \newline
%   \LIV, UK.
%   \\
% \Duration{2015}{2017}  &
%   Vinicius V. Riguete
%   \newline
%   \UERJ, Brazil.
%   \\
% \end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-3em}
\section{Presentations}
\vspace{-1em}
\subsection{Invited Presentations}
\vspace{-1em}
\begin{EntriesTable}
\Year{2026 \newline\footnotesize{March}}  &
  \textbf{Investigating archaeological information commons as coordinated, collective and community-driven action}  
  \newline
  \href{https://sites.google.com/york.ac.uk/dah-lab}{Digital Archaeology and Heritage Lab} Digital Lunch Series
  \newline
  Department of Archaeology, University of York
  \\
\Year{2025 \newline\footnotesize{December}}  &
  \textbf{Archaeological Data Work in Practice}
  \newline
  Digital Heritage Seminar
  \newline
  Instructed by Piraye Hacıgüzeller
  \newline
  Antwerp Cultural Heritage Sciences (ARCHES), University of Antwerp
  \\
\Year{2025 \newline\footnotesize{October}}  &
  \textbf{Open Data in Practice}
  \newline
  INF 649: Digital Curation
  \newline
  Instructed by Ilja Frissen
  \newline
  School of Information Studies, McGill University
  \\
\Year{2025 \newline\footnotesize{April}}  &
  \textbf{Articulating data harmonization as pragmatic, collaborative experiences}
  \newline
  \href{https://mchi.mcgill.ca/}{McGill Clinical and Health Information Research Group}
  \newline
  School of Population and Global Health, McGill University
  \Website{zackbatist.info/CITF-Postdoc/MCHI-2025}
  \\
\Year{2024 \newline\footnotesize{November}}  &
  \textbf{Curating archaeological research data in practice, from the field to the archive}
  \newline
  INF 649: Digital Curation
  \newline
  Instructed by Ilja Frissen
  \newline
  School of Information Studies, McGill University
  \\
\Year{2024 \newline\footnotesize{October}}  &
  \textbf{Exploring collaborative practices in archaeological software development}
  \newline
  A coffee talk for Dr. Jean-Baptiste Poline and colleagues
  \newline
  \href{https://neurodatascience.github.io/}{Neuro Data Science ORIGAMI Lab}, McGill University
\end{EntriesTable}

\vspace{-2em}
\subsection{Conference presentations}
\vspace{-1em}
\begin{EntriesTable}
\Year{2026 \newline\footnotesize{June}}  &
  \Me.
  \textbf{Where do we draw the line? On legitimate uses of AI and open information commons, and commitment to community values.}
  Paper to be presented at the 2026 Implementing New Knowledge Environments (INKE) Gathering.
  Canadian Society for Digital Humanities / Digital Humanities Summer Institute, Université de Montréal.
  \GitHub{zackbatist/inke-2026}
  \Website{zackbatist.info/inke-2026}
  \\
\Year{2026 \newline\footnotesize{April}}  &
  \Me.
  \textbf{BibVik LLM presentation.}
  Paper to be presented at Citational Politics and Practices in Viking Age Archaeology and Beyond.
  Department of Archaeology, Conservation and History, University of Oslo.
  \\
\Year{2026 \newline\footnotesize{April}}  &
  Roe, J., \Me, Yates, J.A.F. { \&} Titolo, A.
  \textbf{archaeo.social and archaeo.dev{:} decentralised, collective digital infrastructure for archaeologists.}
  Poster presented at the 53rd Computer Applications and Quantitative Methods in Archaeology Conference (CAA 2026).
  Vienna, Austria.
  \GitHub{archaeo-social/caa26_archaeo-dev}
  \\
\Year{2023 \newline\footnotesize{December}}  &
  \Me.
  \textbf{Does not compute! Accounting for social and situated experiences while integrating and analyzing obsidian sourcing data.}
  Paper presented at ArcheoFOSS XVII -- Open Science and Archaeology: Archiving the Knowledge. Department of Historical Studies, University of Turin.
  % Turin, Italy.
  \\
\Year{2023 \newline\footnotesize{February}}  &
  \Me.
  \textbf{Documenting the collaborative commitments that support data sharing within archaeological project collectives.}
  Paper presented at Digital Archaeology Bern 2023. Bern Computational and Digital Archaeology lab, University of Bern.
  % Bern, Switzerland.
  \GitHub{zackbatist/DAB23}
  \\
\Year{2021 \newline\footnotesize{June}}  &
  \Me { \&} \JoeRoe.
  \textbf{Open archaeology: a survey of collaborative software engineering in archaeological research.}
  Paper presented at the 49th Computer Applications and Quantitative Methods in Archaeology Conference (CAA 2021).
  Limassol, Cyprus (Virtual).
  \GitHub{zackbatist/caa2021-openarchaeo}
  \\
\Year{2019 \newline\footnotesize{September}}  &
  \Me.
  \textbf{Distributing Knowledge Of Digital Workflows Via Workshops And Support Groups.}
  Lightning talk presented at Our Networks, Re: Infrastructure.
  Toronto.
  \\
\Year{2019 \newline\footnotesize{October}}  &
  \Me.
  \textbf{Untangling and extending the discursive relations mediated by archaeological data through grounded research.}
  Paper presented at On shifting grounds – the study of archaeological practices in a changing world, COST-Arkwork and the Department of History and Archaeology, University of Crete.
  Rethymno, Crete.
  \\
\Year{2018 \newline\footnotesize{April}}  &
  \Me.
  \textbf{Documenting archaeological knowledge construction as socially-embedded information practices.}
  Paper presented at PhD Research Days 2018, Faculty of Information, University of Toronto.
  Toronto, Ontario.
  \\
\Year{2018 \newline\footnotesize{March}}  &
  \Me.
  \textbf{Documenting archaeological knowledge construction as distributed information practices.}
  Paper presented at the 46th Computer Applications and Quantitative Methods in Archaeology Conference (CAA 2018).
  Tübingen, Germany.
  \DOI{10.15496/publikation-87754}
  \\
\Year{2017 \newline\footnotesize{May}}  &
  \Me { \&} \CostisDallas.
  \textbf{A view from the bridge: human- and thing-centred approaches to research practice, disciplinary discourse and local engagement with the archaeological record.}
  Paper presented at TAG (North America) 2017 - The Medium is the Message: Media and Mediation in Archaeology.
  Toronto, Ontario.
  \\
\Year{2017 \newline\footnotesize{March}}  &
  \TristanCarter, \KatieCampeau, \Me, \YosefGarfinkel, \DRosenberg, \YorkRowan { \&} \KatharinaStreit.
  \textbf{Social Interaction at Distance Over the Long Term: Obsidian Sourcing from the Southern Levant (9th – 4th millennia cal BC).}
  Paper presented at the Society for American Archaeology 82nd Annual Meeting.
  Vancouver, British Columbia.
  \\
\Year{2017 \newline\footnotesize{January}}  &
  \Me.
  \textbf{Identifying Obsidian Procurement Habits during the Pre-Pottery Neolithic in the Levant using Network Analysis.}
  Poster presented at the Archaeological Institute of America 118th Annual Meeting.
  Toronto, Ontario.
  \\
\Year{2015 \newline\footnotesize{January}}  &
  \Me.
  \textbf{The Database of Obsidian Sourcing Studies (DObsiSS): Using Git for Collaborative Management of Archaeological Data.}
  Poster presented at the American Archaeological Institute 116th Annual Meeting.
  New Orleans, Louisiana.
  \\
\Year{2014 \newline\footnotesize{March}}  &
  \Me.
  \textbf{An Examination of Obsidian Circulation Patterns in Terms of Relational and Geographical Distance in Southwest Asia and Anatolia from the Epi-Palaeolithic to Chalcolithic Periods (14000 – 5700 B.P.).}
  Paper presented at Archaeological Sciences and the Ancient Mediterranean Environment.
  The Archaeological Centre, University of Toronto.
  \\
\Year{2014 \newline\footnotesize{January}}  &
  \Me.
  \textbf{Using Network Analysis to Examine Relative Resource Procurement Strategies in Anatolia and Southwest Asia from the Epipaleolithic to Chalcolithic Periods (14,000 – 5700 BP).}
  Paper presented at the American Archaeological Institute 115th Annual Meeting.
  Chicago, Illinois.
  \\
\Year{2013 \newline\footnotesize{November}}  &
  \KyleFreund { \&} \Me.
  \textbf{Tracking the Circulation of Sardinian Obsidian using Network Analysis: Lithic Procurement, Cultural Interaction, and Early Maritime Navigation in the Neolithic.}
  Paper presented at Networks of maritime connectivity in the ancient Mediterranean: Structure, continuity, and change over the longue durée. The Archaeology Centre, University of Toronto. Toronto, Ontario.
  \\
\Year{2013 \newline\footnotesize{September}}  &
  \Me.
  \textbf{Using network analysis to examine obsidian assemblage variability in Anatolia and Southwest Asia from the Epi-Palaeolithic to Chalcolithic periods (14000 – 5700 BP).}
  Paper presented at The Future of Historical Network Research Conference. Historical Network Research, University of Hamburg. Hamburg, Germany.
  \\
\Year{2012 \newline\footnotesize{March}}  &
  \Me.
  \textbf{Eat, Drink and Be Networked: Feasting and Bronze Age Networks.}
  Invited panelist at the Colloquium on Digital History and the Transnational History of Nursing. Department of History, Carleton University. Ottawa, Ontario.
\end{EntriesTable}

\vspace{-2em}
\section{Outreach}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2022}{\Ongoing} &
  \textbf{Personal blog}, \href{https://zackbatist.info/posts}{zackbatist.info/posts}
  \newline
  Posts about my research and professional activities
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3em}
\section{Academic Service \& Affiliations}
\vspace{-1em}
% \subsection{Editor}
% \begin{EntriesTable}
% \Duration{2025}{\Ongoing} &
%   \textbf{Drift: Roamings in the Margins of Archaeology}, \href{https://drift-journal.org/}{drift-journal.org}
% \end{EntriesTable}

\subsection{Community leadership}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2026}{\Ongoing} &
  \textbf{Founder and Coordinator}, Digital Archaeology Maintainathon
  % (\href{https://sslarch.github.io/maintainathon}{sslarch.github.io/maintainathon})
  \newline
  An event dedicated to improving archaeological research software and celebrating the often-overlooked work of software maintenance.
  \\
\Year{2025 \newline\footnotesize{Summer}} &
  \textbf{Interim Coordinator} (and member since 2019), Scientific Scripting Languages in Archaeology Special Interest Group (\href{https://sslarch.github.io/}{sslarch.github.io})
  \newline
  Computer Applications in Archaeology
  \\
\Duration{2018}{\Ongoing} &
  \textbf{Founder and Maintainer}, \href{https://open-archaeo.info}{open-archaeo.info}
  \newline
  Index of open source archaeological software and resources
  \\
\Duration{2022}{\Ongoing} &
  \textbf{Community Moderator}, \href{https://about.archaeo.social/}{archaeo.social}
  \newline
  Mastodon instance and social media collective for archaeology
  \\
\Year{2022} &
  \textbf{Peer Mentor}, UofT Coders Peer Mentorship Program
  \newline
  UofT Coders, University of Toronto
  \\
\Duration{2017}{2021} &
  \textbf{Founder and Coordinator}, Archaeological Information Interest Group
  \newline
  The Archaeology Centre, University of Toronto
  \\
\Duration{2013}{2014} &
  \textbf{Webmaster}, Nexus: The Canadian Student Journal of Anthropology
  \newline
  Department of Anthropology, McMaster University
\end{EntriesTable}

\vspace{-2em}
\subsection{Committees}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2019}{2020} &
  \textbf{Graduate Student Union Faculty Representative}
  \newline
  Faculty of Information Doctoral Student Association, University of Toronto
  \\
\Duration{2016}{2019} &
  \textbf{Tech Fund Committee Member and Coordinator}
  \newline
  Faculty of Information Doctoral Student Association, University of Toronto
  \\
\Duration{2013}{2014} &
  \textbf{Graduate Student Association Faculty Representative}
  \newline
  Faculty of Social Sciences, McMaster University
\end{EntriesTable}

% \subsection{Examiner}
% \begin{EntriesTable}
% \Year{2022} &
%   External PhD thesis examiner (Peter Haas), Christian-Albrechts-Universität zu
%   Kiel.
%   \\
% \Year{2022} &
%   Internal PhD thesis examiner (Yael Annemiek Engbers), \LIV.
%   \\
% \Year{2016} &
%   Internal MSc dissertation examiner (Natacha Medeiros Rocha), \UERJ.
% \end{EntriesTable}

\vspace{-2em}
\subsection{Conference \& Panel Organizer}
\vspace{-1em}
\begin{EntriesTable}
\Year{2026 \newline\footnotesize{April}}  &
  \textbf{Citational Politics and Practices in Viking Age Archaeology and Beyond}
  \newline
  Co-organized with Julie Lund { \&} Isak Roalkvam
  \newline
  Department of Archaeology, Conservation and History, University of Oslo
  \newline
  \emph{Discussion about methodological challenges in bibliometric analysis, aspects of reflexivity in Viking Age archaeology, and how computational methods can be leveraged to conduct meaningful meta-research.}
  \Website{zackbatist.info/BibVik/workshop}
  \\
\Year{2023 \newline\footnotesize{December}} &
  \textbf{archaeo.social: archaeology in the Fediverse and the future of scholarly social media}
  \newline
  Panel convened for \href{https://www.archeofoss.org/2023/}{ArcheoFOSS XVII} with Joe Roe
  \newline
  Department of Historical Studies, University of Turin
  \GitHub{archaeo-social/archeofoss23_fediverse}
  \DOI{10.5281/zenodo.10362684}
  \\
\Year{2014} &
  \textbf{Second Annual Interdisciplinary Colloquium}
  \newline
  Co-organized with Priscilla Medeiros
  \newline
  Faculty of Social Sciences, McMaster University
\end{EntriesTable}

\vspace{-2em}
\subsection{Interest Groups}
\vspace{-1em}
\begin{EntriesTable}
\Duration{2018}{2022} &
  UofT Coders (\href{https://uoftcoders.github.io/studyGroup/}{uoftcoders.github.io})
  \newline
  University of Toronto
  \\
\Duration{2018}{2019} &
  Digitality Reading Group
  \newline
  University of Toronto
  \\
\Duration{2017}{2019} &
  Archaeological Theory Interest Group
  \newline
  The Archaeology Centre, University of Toronto
  \\
\Duration{2017}{2021} &
  Archaeological Information Interest Group
  \newline
  The Archaeology Centre, University of Toronto
\end{EntriesTable}

\vspace{-2em}
\subsection{Certifications}
\begin{itemize}
  \item The Carpentries Instructor Training
\end{itemize}

\subsection{Reviewer}
\begin{itemize}
  \item Open Information Science
  \item Computer Applications in Archaeology
  \item Peer Community in Archaeology
  \item Advances in Archaeological Practice
\end{itemize}

\section{Languages}
\vspace{-1em}
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.1\textwidth} p{0.85\textwidth}@{}}
  \textbf{English} & Mother tongue
  \\
  \textbf{French}  & Basic reading and writing
\end{tabularx}

\end{document}
