% !TEX program = xelatex
\documentclass[11pt, a4paper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}

% Identifying information
\newcommand{\FirstName}{Zachary}
\newcommand{\LastName}{Batist}
\newcommand{\Initials}{Z}
\newcommand{\MyName}{\FirstName\ \LastName}

\newcommand{\Email}{zacharybatist@gmail.com}
\newcommand{\PersonalWebsite}{zackbatist.info}
\newcommand{\MyGitHub}{zackbatist}
\newcommand{\Twitter}{@mtl\_zack}
\newcommand{\Mastodon}{archaeo.social/@zackbatist}
\newcommand{\ORCID}{0000-0003-0435-508X}
%\newcommand{\Address}{4653 Rue Clark \\ Montreal, Quebec, Canada \\ H2T 2T3}
\newcommand{\Address}{\phantom{text} \\ \phantom{text} \\ \phantom{text}}
\newcommand{\UTorontoAddress}{Bissell Building, 140 St. George Street \\ M5S 3G6, Toronto, Ontario, Canada}
\newcommand{\Affiliation}{\TORINF \\ \TOR}
\newcommand{\TORINF}{Faculty of Information}
\newcommand{\Title}{Curriculum Vit\ae}
%\newcommand{\LabWebsite}{compgeolab.org}

% Names for citing coauthors
\newcommand{\Me}{\LastName, \Initials}
\newcommand{\CostisDallas}{Dallas, C}
\newcommand{\ValMasters}{Masters, V}
\newcommand{\TiffanyTorma}{Torma, TC}
\newcommand{\NielFerris}{Ferris, N}
\newcommand{\IstoHuvila}{Huvila, I}
\newcommand{\SeamusRoss}{Ross, S}
\newcommand{\MichaelCarter}{Carter, WM}
\newcommand{\TristanCarter}{Carter, T}
\newcommand{\DanContreras}{Contreras, D}
\newcommand{\CiaraZogheib}{Zogheib, C}
\newcommand{\KatieCampeau}{Campeau, K}
\newcommand{\YosefGarfinkel}{Garfinkel, Y}
\newcommand{\KatharinaStreit}{Streit, K}
\newcommand{\KyleFreund}{Freund, KP}
\newcommand{\ShawnGraham}{Graham, S}
\newcommand{\NehaGupta}{Gupta, N}
\newcommand{\JoleneSmith}{Smith, J}
\newcommand{\AndreasAngourakis}{Angourakis, A}
\newcommand{\AndrewReinhard}{Reinhard, A}
\newcommand{\KateEllenberger}{Ellenberger, K}
\newcommand{\JoelRivard}{Rivard, J}
\newcommand{\BenMarwick}{Marwick, B}
\newcommand{\BethCompton}{Compton, B}
\newcommand{\RobBlades}{Blades, R}
\newcommand{\CristinaWood}{Wood, C}
\newcommand{\GaryNobles}{Nobles, G}
\newcommand{\JoeRoe}{Roe, J}
\newcommand{\DRosenberg}{Rosenberg, D}
\newcommand{\YorkRowan}{Rowan, Y}
\newcommand{\MartinLoignon}{Loignon, M}
\newcommand{\WeiminMiao}{Miao, W}
\newcommand{\LianggaoHu}{Hu, L}
\newcommand{\AndrewBier}{Bier, A}
\newcommand{\TarekBismar}{Bismar, TA}
\newcommand{\JamesScrivens}{Scrivens, PJ}
\newcommand{\KorenMann}{Mann, K}
\newcommand{\MarkBasik}{Basik, M}
\newcommand{\AmelieBouchard}{Bouchard, A}
\newcommand{\PierreFiset}{Fiset, PO}
\newcommand{\GeraldBatist}{Batist, G}

% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.12\textwidth}@{\hspace{0.02\textwidth}}p{0.86\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{\newline \aiDoi\ \href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{\newline \faGithub\ \href{https://github.com/#1}{\detokenize{#1}}}
\newcommand{\Gist}[1]{\newline \faGithub\ \href{https://gist.github.com/#1}{#1}}
\newcommand{\Website}[1]{\newline \faGlobe\ \href{https://#1}{#1}}
\newcommand{\ZenodoDOI}[1]{\newline \aiZenodo\ \href{https://doi.org/#1}{#1}}
\newcommand{\Slides}[1]{\newline • Slides: \faTv\ \href{https://#1}{#1}}
\newcommand{\SlidesDOI}[1]{\newline • Slides: \faTv\ \DOILink{#1}}
\newcommand{\PosterDOI}[1]{\newline • Poster: \faImage\ \DOILink{#1}}
\newcommand{\OA}{\aiOpenAccess\enspace}
\newcommand{\Invited}{\newline • \textbf{Invited talk}}
\newcommand{\Role}[1]{\newline • Role: #1}
\newcommand{\Preprint}[1]{\newline \faParagraph\ \href{https://doi.org/#1}{#1}}
\newcommand{\Note}[1]{\newline \faExclamationCircle\ {#1}}
\newcommand{\Youtube}[1]{\newline • Recording: \faYoutube\ \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}


% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont #1 -- #2}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\Ongoing}{present}
%\newcommand{\Ongoing}{$\ast$}
\newcommand{\Future}{future}
\newcommand{\Review}{in review}
\newcommand{\Press}{in press}
\newcommand{\Progress}{In progress}
\newcommand{\Accepted}{accepted}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3 \newline #4}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[a4paper,margin=1.5cm,includehead,headsep=2mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
\usepackage{fontspec}  % required to make older xelatex compile with UTF8

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.5cm}\bfseries\fontsize{12pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.2cm}\mdseries\fontsize{12pt}{0}\selectfont\uppercase}

% Set the spacing for sections
%\usepackage{titlesec}
%\titlespacing{\section}{0pt}{0cm}{0.3cm}
%\titlespacing{\subsection}{0pt}{0.3cm}{0.3cm}

% Disable number of sections. Use this instead of "section*" so that the sections still appear as PDF bookmarks. Otherwise, would have to add the table of contents entries manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
  \fontsize{10pt}{12pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
  \hspace{0.2cm} -- \hspace{0.2cm}
  \monthyear\today
}
\rhead{\fontsize{10pt}{0}\selectfont \thepage/\pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
{\fontsize{22pt}{0}\selectfont\MyName}\\[-1.5cm]
\begin{minipage}[t]{1\textwidth}
  \begin{flushright}
    % Last updated: \monthyear\today\\
    Website: \href{https://\PersonalWebsite}{\PersonalWebsite}\\
    ORCID: \href{https://orcid.org/\ORCID}{\ORCID}\\
    Email: \href{mailto:\Email}{\Email}
    %GitHub: \href{https://github.com/\MyGitHub}{\MyGitHub}\\
    % Mastodon: \href{https://\Mastodon}{\Mastodon}\\
    % Twitter: \href{https://\Twitter}{\Twitter}
  \end{flushright}
\end{minipage}\\[0.1cm]
\rule{\textwidth}{0.2pt}\\[-1cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Professional Appointments}

% \begin{EntriesTable}
%   \Duration{2018}{\Ongoing}  &
%   \Appointment{Affiliate Researcher}{\UHEARTH}{\SOEST}{\UHM, USA}
%   \\
%   \Duration{2017}{2018}  &
%   \Appointment{Visiting Research Scholar}{\UHEARTH}{\SOEST}{\UHM, USA}
%   \\
%   \Duration{2014}{2018}  &
%   \Appointment{Assistant Professor}{Departamento de Geologia Aplicada}{Faculdade de Geologia}{\UERJ, Brazil}
% \end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\begin{EntriesTable}
\Year{2023}  &
  \textbf{PhD}, Faculty of Information, University of Toronto
  \newline
  \href{https://tspace.library.utoronto.ca/handle/1807/130306}{Archaeological data work as continuous and collaborative practice}
  \\
\Year{2014}  &
  \textbf{MA}, Department of Anthropology, McMaster University
  \newline
  \href{https://macsphere.mcmaster.ca/handle/11375/16528}{Obsidian Circulation Networks in Southwest Asia and Anatolia: A Comparative Approach}
  \\
\Year{2012}  &
  \textbf{BA}, Directed Interdisciplinary Studies, Carleton University
  %\newline
  %Feasting In Bronze Age Greece: A Network Analysis Approach
  \\
\Year{2009}  &
  \textbf{DEC}, Social Sciences, Dawson College\\[-0.5cm]
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grants \& Fellowships}
\begin{EntriesTable}
\Duration{2019}{2021}  &
  \textbf{SSHRC Doctoral Fellowship}. Archaeological data curation as continuous and collaborative practice. Award ID: {752-2019-2233}.\\[-0.5cm]
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research positions}
\begin{EntriesTable}
\Duration{2018}{2023}  &
  \textbf{Research Assistant}
  \newline
  E{\textendash}CURATORS: Pervasive Digital Curation Activities, Objects and Infrastructures in Archaeological Research and Communication
  \newline
  Faculty of Information, University of Toronto
  \\
\Duration{2016}{2021}  &
  \textbf{Database Manager}
  \newline
  Stelida Naxos Archaeology Project
  \\
\Year{2009}  &
  \textbf{Research Assistant}
  \newline
  Redpath Museum, McGill University
  \\
\Duration{2007}{2009}  &
  \textbf{Research Assistant}
  \newline
  Molecular Pharmacology Laboratory
  \newline
  Lady Davis Institute for Medical Research\\[-0.5cm]
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\subsection{Journal articles}
\begin{EntriesTable}
\Year{In press}  &
  \Me.
  \textbf{Does not compute! Accounting for social and situated experiences while integrating and analyzing obsidian sourcing data.}
  Archeologia e Calcolatori. (special issue comprising papers presented at ArcheoFOSS XVII).
  35(2).%:xxxx-xxxx.
  \DOI{10.19282/ac.35.2.2024.00}
\\
\Year{2024}  &
  \Me.
  \textbf{On the Value of Informal Communication in Archaeological Data Work.}
  Open Archaeology.
  10(1):20240014.
  \DOI{10.1515/opar-2024-0014}
\\
\Year{2024}  &
  \Me { \&} \JoeRoe.
  \textbf{Open archaeology, open source? Collaborative practices in an emerging community of archaeological software engineers.}
  Internet Archaeology
  67.
  \DOI{10.11141/ia.67.13}
  \GitHub{zackbatist/openarchaeo-collaboration}
  % \Website{zackbatist.info/openarchaeo-collaboration} (postprint)
  % \ZenodoDOI{10.5281/zenodo.12752060}
\\
\Year{2023}  &
  \Me { \&} \JoeRoe.
  \textbf{Open-archaeo: a resource for documenting archaeological software development practices.}
  Journal of Open Archaeology Data.
  11(9):1-7.
  \DOI{10.5334/joad.111}
  \\
\Year{2021}  &
  \Me, \ValMasters, \TiffanyTorma, \NielFerris, \IstoHuvila, \SeamusRoss, \MichaelCarter { \&} \CostisDallas.
  \textbf{Figurations of Digital Archaeological Practice in Two Mediterranean Fieldwork Projects.}
  Open Archaeology (Special Issue on Archaeological Practice on Shifting Grounds)
  7(1):1731-1755.
  \DOI{10.1515/opar-2020-0217}
  %\ZenodoDOI{10.5281/zenodo.5831760}
  \\
\Year{2021}  &
  \DanContreras, \Me, \CiaraZogheib { \&} \TristanCarter.
  \textbf{Matching Pragmatic Lithic Analysis and Proper Data Architecture: The QuARI R Shiny Database Interface.}
  Advances in Archaeological Practice
  9(4):299-311.
  \DOI{10.1017/aap.2021.11}
  \GitHub{zackbatist/QuARI}
  \\
\Year{2017}  &
  \TristanCarter, \Me, \KatieCampeau, \YosefGarfinkel { \&} \KatharinaStreit.
  \textbf{Investigating Pottery Neolithic Socio-Economic “Regression” in the Southern Levant: Characterising Obsidian Consumption at Sha’ar Hagolan (N. Israel).}
  Journal of Archaeological Science: Reports
  15:305-317.
  \DOI{10.1016/j.jasrep.2017.08.016}
  \\
\Year{2014}  &
  \KyleFreund { \&} \Me.
  \textbf{Sardinian Obsidian Circulation and Early Maritime Navigation in the Neolithic as Shown through Social Network Analysis.}
  Journal of Island and Coastal Archaeology
  9(3):364-380.
  \DOI{10.1080/15564894.2014.881937}
  \\
\Year{2009}  &
  \MartinLoignon, \WeiminMiao, \LianggaoHu, \AmelieBouchard, \TarekBismar, \JamesScrivens, \KorenMann, \MarkBasik, \PierreFiset, \Me { \&} \GeraldBatist.
  \textbf{Frequent Nrf2 depletion due to Cul3 overexpression in breast cancer is associated with sensitivity to carcinogens, oxidative stress and chemotherapy.}
  Molecular Cancer Therapeutics
  8(8):2432-2440.
  \DOI{10.1158/1535-7163.MCT-08-1186}
\end{EntriesTable}

\subsubsection{Articles in Progress}
\begin{EntriesTable}
\Year{\Review}  &
  \Me.
  \textbf{Locating creative agency in archaeological data work.}
  Cambridge Archaeological Journal.
\\
\Year{\Review}  &
  \Me.
  \textbf{Balancing situated and objective representations in archaeological fieldwork.}
  Advances in Archaeological Practice.
\\
% \Year{\Progress}  &
%   \Me.
%   \textbf{Scaffolding archaeological projects through data management protocols.}\newline
%   \emph{Articulates the social and technical apparatus that govern how specialist work and information are distributed throughout an archaeological project.}\\
  \Year{\Progress}  &
  \Me.
  \textbf{The situation of data papers in archaeological knowledge production.}\newline
  \emph{Traces how published archaeological datasets are situated within broader citation networks, through empirical analysis of open bibliometric metadata.}\\
% \Year{\Progress}  &
%   \Me.
%   \textbf{Distribution and internalization of roles in distributed and multi-stakeholder projects.}\newline
%   \emph{Articulates a theory of role-relations in cooperative work environments that I developed throughout my PhD.}\\
% \Year{\Progress}  &
%   \Me.
%   \textbf{Open data, overstated: an exploration of small-scale, offline and private acts of data-sharing within archaeological projects.}\newline
%   \emph{Framing archaeological knowledge production in terms participating as a member of a commons, and accounting for the roles, relationships and boundaries that commoning entails.}\\
\Year{\Progress}  &
\JoeRoe { \&} \Me.
  \textbf{Archaeology in the fediverse: reclaiming ownership of scholarly social media.}\newline
  \emph{Position paper articulating the discussion held during our panel at ArcheoFOSS XVII.}
\end{EntriesTable}

\subsection{Book contributions}
\begin{EntriesTable}
\Year{2018}  &
  \ShawnGraham, \NehaGupta, \JoleneSmith, \AndreasAngourakis, \AndrewReinhard, \KateEllenberger, \Me, \JoelRivard, \BenMarwick, \MichaelCarter, \BethCompton, \RobBlades, \CristinaWood { \&} \GaryNobles.
  \textbf{The Open Digital Archaeology Textbook.}
  eCampus Ontario.
  \Website{o-date.github.io}\newline
  \faIcon{award}\ Award for Outstanding Work in Digital Archaeology, Archaeological Institute of America
\end{EntriesTable}

% \subsection{Conference proceedings}
% \begin{EntriesTable}
% \Year{2022}  &
%   \Me.
%   Documenting archaeological knowledge construction as information practices.
%   \emph{Proceedings of the 46th Conference on Computer Applications and Quantitative Methods in Archaeology},
%   \DOI{XXXX}
%   \\
% \end{EntriesTable}

\subsection{Open-source Software}
\begin{EntriesTable}
\Duration{2020}{2021} &
  \textbf{Queryable Artefact Record Interface (QuARI)}
  \newline
  A database interface designed to facilitate the irregular, iterative, and non-linear workflows that are commonly employed in lithic analysis.
  \GitHub{zackbatist/QuARI}
\end{EntriesTable}

\subsection{Open Datasets}
\begin{EntriesTable}
\Duration{2018}{\Ongoing}  &
  \textbf{open-archaeo}
  A comprehensive list of open source archaeological software and resources.
  \DOI{10.5281/zenodo.8299651}
  \GitHub{zackbatist/open-archaeo}
  \Website{open-archaeo.info}
  \\
\Duration{2014}{2017}  &
  \textbf{The Database of Obsidian Sourcing Studies (DObsiSS)}
  A listing of chemically characterized archaeological obsidian, compiled from published journal articles, excavation reports, conference papers and other scholarly records.
  \DOI{10.5281/zenodo.55848}
  \GitHub{zackbatist/DObsiSS}
  \Website{zackbatist.info/DObsiSS}
\end{EntriesTable}

% \section{Presentations}

\subsection{Conference presentations}
\begin{EntriesTable}
\Year{2023}  &
  \Me.
  \textbf{Does not compute! Accounting for social and situated experiences while integrating and analyzing obsidian sourcing data.}
  Paper presented at ArcheoFOSS XVII -- Open Science and Archaeology: Archiving the Knowledge. Department of Historical Studies, University of Turin.
  Turin, Italy, 12-13 December 2023.
  %LINK
  \\
\Year{2023}  &
  \Me.
  \textbf{Documenting the collaborative commitments that support data sharing within archaeological project collectives.}
  Paper presented at Digital Archaeology Bern 2023. Bern Computational and Digital Archaeology lab, University of Bern.
  Bern, Switzerland, 1-3 February 2023.
  \GitHub{zackbatist/DAB23}
  \\
\Year{2021}  &
  \Me { \&} \JoeRoe.
  \textbf{Open archaeology: a survey of collaborative software engineering in archaeological research.}
  Paper presented at the 49th Computer Applications and Quantitative Methods in Archaeology Conference (CAA 2021).
  Limassol, Cyprus (Virtual), 14-18 June 2021.
  \GitHub{zackbatist/caa2021-openarchaeo}
  \\
\Year{2019}  &
  \Me.
  \textbf{Distributing Knowledge Of Digital Workflows Via Workshops And Support Groups.}
  Lightning talk presented at Our Networks, Re: Infrastructure.
  Toronto, Ontario, September 20–22, 2019
  \\
\Year{2019}  &
  \Me.
  \textbf{Untangling and extending the discursive relations mediated by archaeological data through grounded research.}
  Paper presented at On shifting grounds – the study of archaeological practices in a changing world, COST-Arkwork and the Department of History and Archaeology, University of Crete.
  Rethymno, Crete, October 2019.
  \\
\Year{2018}  &
  \Me.
  \textbf{Documenting archaeological knowledge construction as socially-embedded information practices.}
  Paper presented at PhD Research Days 2018, Faculty of Information, University of Toronto.
  Toronto, Ontario, April 2018.
  \\
\Year{2018}  &
  \Me.
  \textbf{Documenting archaeological knowledge construction as distributed information practices.}
  Paper presented at the 46th Computer Applications and Quantitative Methods in Archaeology Conference (CAA 2018).
  Tübingen, Germany, March 2018.
  \DOI{10.15496/publikation-87754}
  \\
\Year{2017}  &
  \Me { \&} \CostisDallas.
  \textbf{A view from the bridge: human- and thing-centred approaches to research practice, disciplinary discourse and local engagement with the archaeological record.}
  Paper presented at TAG (North America) 2017 - The Medium is the Message: Media and Mediation in Archaeology.
  Toronto, Ontario, May 2017.
  \\
\Year{2017}  &
  \TristanCarter, \KatieCampeau, \Me, \YosefGarfinkel, \DRosenberg, \YorkRowan { \&} \KatharinaStreit.
  \textbf{Social Interaction at Distance Over the Long Term: Obsidian Sourcing from the Southern Levant (9th – 4th millennia cal BC).}
  Paper presented at the Society for American Archaeology 82nd Annual Meeting.
  Vancouver, British Columbia, March – April 2017.
  \\
\Year{2017}  &
  \Me.
  \textbf{Identifying Obsidian Procurement Habits during the Pre-Pottery Neolithic in the Levant using Network Analysis.}
  Poster presented at the Archaeological Institute of America 118th Annual Meeting.
  Toronto, Ontario, January 2017.
  \\
\Year{2015}  &
  \Me.
  \textbf{The Database of Obsidian Sourcing Studies (DObsiSS): Using Git for Collaborative Management of Archaeological Data.}
  Poster presented at the American Archaeological Institute 116th Annual Meeting.
  New Orleans, Louisiana, January 2015.
  \\
\Year{2014}  &
  \Me.
  \textbf{An Examination of Obsidian Circulation Patterns in Terms of Relational and Geographical Distance in Southwest Asia and Anatolia from the Epi-Palaeolithic to Chalcolithic Periods (14000 – 5700 B.P.).}
  Paper presented at Archaeological Sciences and the Ancient Mediterranean Environment.
  The Archaeological Centre, University of Toronto, March 2014.
  \\
\Year{2014}  &
  \Me.
  \textbf{Using Network Analysis to Examine Relative Resource Procurement Strategies in Anatolia and Southwest Asia from the Epipaleolithic to Chalcolithic Periods (14,000 – 5700 BP).}
  Paper presented at the American Archaeological Institute 115th Annual Meeting.
  Chicago, Illinois, January 2014.
  \\
\Year{2013}  &
  \KyleFreund { \&} \Me.
  \textbf{Tracking the Circulation of Sardinian Obsidian using Network Analysis: Lithic Procurement, Cultural Interaction, and Early Maritime Navigation in the Neolithic.}
  Paper presented at Networks of maritime connectivity in the ancient Mediterranean: Structure, continuity, and change over the longue durée. The Archaeology Centre, University of Toronto. Toronto, Ontario, November 2013.
  \\
\Year{2013}  &
  \Me.
  \textbf{Using network analysis to examine obsidian assemblage variability in Anatolia and Southwest Asia from the Epi-Palaeolithic to Chalcolithic periods (14000 – 5700 BP).}
  Paper presented at The Future of Historical Network Research Conference. Historical Network Research, University of Hamburg. Hamburg, Germany, September 2013.
  \\
\Year{2012}  &
  \Me.
  \textbf{Eat, Drink and Be Networked: Feasting and Bronze Age Networks.}
  Invited panelist at the Colloquium on Digital History and the Transnational History of Nursing. Department of History, Carleton University. Ottawa, Ontario, March 2012.
\end{EntriesTable}

% \subsection{Other}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards \& Honors}
\begin{EntriesTable}
\Year{2019}  &
  \textbf{Research Travel Grant} (\$500)
  \newline
  Faculty of Arts and Science, University of Toronto
  \\
\Year{2017}  &
  \textbf{Joseph and Maria Shaw Graduate Student Travel Award} (\$500)
  \newline
  The Archaeology Centre, University of Toronto
  \\
\Year{2015}  &
  \textbf{McMaster University Travel Scholarship for OpenCon 2015} (\$2500)
  \newline
  McMaster University Library, McMaster University
  \\
\Year{2015}  &
  \textbf{Edith M. Wightman Travel Scholarship} (\$1000)
  \newline
  School of Graduate Studies, McMaster University
  \\
\Year{2015}  &
  \textbf{Travel Assistance Grant} (\$500)
  \newline
  School of Graduate Studies, McMaster University
  \\
\Year{2015}  &
  \textbf{Graduate Student Travel Award} (\$120)
  \newline
  Archaeological Institute of America
  \\
\Year{2014}  &
  \textbf{Robert P. Wolff Thesis Prize}
  \newline
  Society for Philosophy \& Culture, McMaster University
  \\
\Year{2014}  &
  \textbf{McMaster University Travel Scholarship for OpenCon 2014} (\$2500, declined)
  \newline
  McMaster University Library, McMaster University
  \\
\Year{2012}  &
  \textbf{Dean's Honour List}
  \newline
  Carleton University
  \\
\Year{2012}  &
  \textbf{Michael Kelway Oliver Scholarship} (\$2000)
  \newline
  Carleton University
  \\
\Year{2011}  &
  \textbf{Full Tuition Scholarship} (declined)
  \newline
  Digital Humanities Summer Institute, University of Victoria
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching}
\subsection{Teaching Assistant}
\begin{EntriesTable}
\Year{2020}  &
  \textbf{Curatorial Practice}
  (MSL 2000)
  \newline
  Faculty of Information, University of Toronto
  \\
\Duration{2017}{2020}  &
  \textbf{Representing, Documenting, and Accessing the Cultural Record}
  (INF 1321)
  \newline
  Faculty of Information, University of Toronto
  \\
\Year{2017}  &
  \textbf{Information Policy, Regulation and Law}
  (INF 2181)
  \newline
  Faculty of Information, University of Toronto
  \\
\Year{2016}  &
  \textbf{Archaeology and Popular Culture}
  (ANTH 2PC3)
  \newline
  Department of Anthropology, McMaster University
  \\
\Duration{2014}{2015}  &
  \textbf{World Archaeology}
  (ANTH 2WA3E)
  \newline
  Department of Anthropology, McMaster University
  \\
\Year{2012, 2015}  &
  \textbf{Introduction to Anthropology: Identity, Race and Power}
  (ANTH 1AB3E)
  \newline
  Department of Anthropology, McMaster University
  \\
\Year{2013}  &
  \textbf{Introduction to Anthropology: Sex, Food and Death}
  (ANTH 1AA3)
  \newline
  Department of Anthropology, McMaster University
\end{EntriesTable}

\subsection{Workshops \& Short Courses}
\begin{EntriesTable}
\Year{2022}  &
  \textbf{Using Qualitative Data Analysis Software}
  \newline
  The Ethnography Lab Methods Café: Software in Ethnographic Research Methods
  \newline
  Department of Anthropology, University of Toronto
  \\
\Year{2018}  &
  \textbf{Designing and Implementing Relational Databases}
  \newline
  Archaeological Information Interest Group
  \newline
  The Archaeology Centre, University of Toronto
  \GitHub{zackbatist/archaeo-db-workshop}
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Student supervision}
% \subsection{P\lowercase{h}D \lowercase{(main advisor)}}
% \begin{EntriesTable}
% \Duration{2021}{\Ongoing}  &
%   India Uppal
%   \newline
%   \LIV, UK.
%   \newline
%   Co-advisors: Vanderlei C. Oliveira Jr., Richard Holme
% \end{EntriesTable}

% \subsection{P\lowercase{h}D \lowercase{(co-advisor)}}
% \begin{EntriesTable}
% \Duration{2021}{\Ongoing}  &
%   Gelson Ferreira de Souza Junior
%   \newline
%   Universidade de São Paulo, Brazil.
%   \newline
%   Advisor: Ricardo I.F. Trindade
%   \\
% \Duration{2017}{2022}  &
%   Santiago R. Soler
%   \newline
%   Universidad Nacional de San Juan, Argentina.
%   \newline
%   Advisor: Mario E. Gimenez
% \end{EntriesTable}

% \subsection{Master's}
% \begin{EntriesTable}
% \Duration{2020}{2021}  &
%   Aidan Hernaman
%   \newline
%   \LIV, UK.
% \end{EntriesTable}

% \subsection{Undergraduate}
% \begin{EntriesTable}
% \Duration{2021}{2022}  &
%   Sarah Askevold, Laura Nicholls, and Hamed R.H. Al-Salehi
%   \newline
%   \LIV, UK.
%   \\
% \Duration{2020}{2021}  &
%   Majed M.A. Abura, Ali A.A. Alhazmi, Daniel P. Gilbert, and Mustafa M.M.
%   Alordowny
%   \newline
%   \LIV, UK.
%   \\
% \Duration{2019}{2020}  &
%   Lottie Cooper, Steven Heer, Charles Thomson, and Alexander Borges
%   \newline
%   \LIV, UK.
%   \\
% \Duration{2015}{2017}  &
%   Vinicius V. Riguete
%   \newline
%   \UERJ, Brazil.
%   \\
% \end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Outreach}
\begin{EntriesTable}
\Duration{2022}{\Ongoing} &
  \textbf{Personal blog}, \href{https://blog.zackbatist.info}{blog.zackbatist.info}
  \newline
  Posts about my research and professional activities
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Service \& Affiliations}
% \subsection{Editor}
% \begin{EntriesTable}
%   \Duration{2019}{\Ongoing} & Topic editor for the \textit{Journal of Open Source Software}
% \end{EntriesTable}

\subsection{Community leadership}
\begin{EntriesTable}
\Duration{2018}{\Ongoing} &
  \textbf{Founder and Maintainer}, \href{https://open-archaeo.info}{open-archaeo.info}
  \newline
  Index of open source archaeological software and resources
  \\
\Duration{2022}{\Ongoing} &
  \textbf{Community Moderator}, \href{https://about.archaeo.social/}{archaeo.social}
  \newline
  Mastodon instance and social media collective for archaeology
  \\
\Year{2022} &
  \textbf{Peer Mentor}, UofT Coders Peer Mentorship Program
  \newline
  UofT Coders, University of Toronto
  \\
\Duration{2017}{2021} &
  \textbf{Founder and Coordinator}, Archaeological Information Interest Group
  \newline
  The Archaeology Centre, University of Toronto
  \\
\Duration{2013}{2014} &
  \textbf{Webmaster}, Nexus: The Canadian Student Journal of Anthropology
  \newline
  Department of Anthropology, McMaster University
\end{EntriesTable}

\subsection{Committees}
\begin{EntriesTable}
\Duration{2019}{2020} &
  \textbf{Graduate Student Union Faculty Representative}
  \newline
  Faculty of Information Doctoral Student Association, University of Toronto
  \\
\Duration{2016}{2019} &
  \textbf{Tech Fund Committee Member and Coordinator}
  \newline
  Faculty of Information Doctoral Student Association, University of Toronto
  \\
\Duration{2013}{2014} &
  \textbf{Graduate Student Association Faculty Representative}
  \newline
  Faculty of Social Sciences, McMaster University
\end{EntriesTable}

% \subsection{Examiner}
% \begin{EntriesTable}
% \Year{2022} &
%   External PhD thesis examiner (Peter Haas), Christian-Albrechts-Universität zu
%   Kiel.
%   \\
% \Year{2022} &
%   Internal PhD thesis examiner (Yael Annemiek Engbers), \LIV.
%   \\
% \Year{2016} &
%   Internal MSc dissertation examiner (Natacha Medeiros Rocha), \UERJ.
% \end{EntriesTable}

\subsection{Conference \& Panel Organizer}
\begin{EntriesTable}
\Year{2023} &
  \textbf{archaeo.social: archaeology in the Fediverse and the future of scholarly social media}
  \newline
  Panel convened for \href{https://www.archeofoss.org/2023/}{ArcheoFOSS XVII} with Joe Roe
  \newline
  Department of Historical Studies, University of Turin
  \GitHub{archaeo-social/archeofoss23_fediverse}
  \DOI{10.5281/zenodo.10362684}
  \\
\Year{2014} &
  \textbf{Second Annual Interdisciplinary Colloquium}
  \newline
  Co-organized with Priscilla Medeiros
  \newline
  Faculty of Social Sciences, McMaster University
\end{EntriesTable}

\subsection{Interest Groups}
\begin{EntriesTable}
\Duration{2018}{\Ongoing} &
  Scientific Scripting Languages in Archaeology Special Interest Group (\href{https://sslarch.github.io/}{sslarch.github.io})
  \newline
  Computer Applications in Archaeology
  \\
\Duration{2018}{2022} &
  UofT Coders (\href{https://uoftcoders.github.io/studyGroup/}{uoftcoders.github.io})
  \newline
  University of Toronto
  \\
\Duration{2018}{2019} &
  Digitality Reading Group
  \newline
  University of Toronto
  \\
\Duration{2017}{2019} &
  Archaeological Theory Interest Group
  \newline
  The Archaeology Centre, University of Toronto
  \\
\Duration{2017}{2021} &
  Archaeological Information Interest Group
  \newline
  The Archaeology Centre, University of Toronto
\end{EntriesTable}

\subsection{Certifications}
\begin{itemize}
  \item The Carpentries Instructor Training
\end{itemize}

\subsection{Reviewer}
\begin{itemize}
  \item Open Information Science
  \item Computer Applications in Archaeology
\end{itemize}

\section{Languages}
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.1\textwidth} p{0.85\textwidth}@{}}
  \textbf{English} & Mother tongue
  \\
  \textbf{French}  & Basic reading and writing
\end{tabularx}

\end{document}
